---
title: "Karate Statistics Around the World"
description: |
  This project examines different graphs that analyze statistics about Martial Arts in different countries!
author:
  - name: Amisha Jain
site: distill::distill_website
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse)
library(rvest)
library(plotly)
library(janitor)
library(tidyr)
library(knitr)

# Learn more about creating websites with Distill at:
# https://rstudio.github.io/distill/website.html

# Learn more about publishing to GitHub Pages at:
# https://rstudio.github.io/distill/publish_website.html#github-pages

```

**Karate Instructors**


*Note: This graph is interactive so click on a point to get more information!*


```{r find_url, echo = FALSE}
web_url <- "https://www.zippia.com/martial-arts-instructor-jobs/demographics/"

pick_data <- web_url |> read_html() |> 
  html_elements("table") |> 
  html_table()

#I want to pick the non-table. Figure that part out.
```

```{r cleaning_data, echo = FALSE}
fix_code <- pick_data[[2]] |> 
  pivot_longer(cols = c(Male, Female), names_to = "Gender") |> 
  mutate(Year = as.integer(Year)) |> 
  rename(year = Year) |> 
  mutate(year = as.character(year)) |> 
  mutate(year = substr(year, 1, 4))
  
```


```{r plot_data, echo = FALSE}
set_data <- fix_code |> 
  ggplot(aes(x = year, y = value, fill = Gender)) + 
  geom_point() + theme_classic() +
  labs(title = "Number of Martial Arts Instructors per Year by Gender", 
       subtitle = "Every year there were more male instructors than female", 
       x = "Year", y = "Percentage of Instructors", 
       caption = "Source: Zippia -- The Career Expert") + 
 scale_x_discrete(guide = guide_axis(angle = 45))

ggplotly(set_data, tooltip = "all")

#what kind of graph do I want?
```

#### The source is Zippia -- The Career Expert.

The graph above demonstrates how there are less female instructors than male every year. As shown in the plot, the percentage of female instructors was always around 20% while male instructors was around 75%. This brings up the questions of why women aren't as involved in this sport and how this can increase around the world. This statistic is specifically from 2010 to 2019 in the United States.




**World Karate Championships**

```{r pick_url, echo = FALSE}
web_url <- "https://en.wikipedia.org/wiki/World_Cadet,_Junior_and_U21_Karate_Championships"

source_data <- web_url |> read_html() |> 
html_elements("table") |> html_table()

```

```{r fixing_up, echo = FALSE}
source_data[[4]] |> 
  slice(1:20) |> ggplot(aes(x = fct_reorder(Nation, Rank), 
                            y = Total, fill = Gold)) + 
  geom_col() + scale_x_discrete(guide = guide_axis(angle = 45)) +
  theme_classic() + 
  labs(title = "Countries in World Karate Championships Ranked by Medals", 
       subtitle = "Japan is #1 with most gold but not the most total medals", 
       x = "Countries", y = "Total Number of Medals", 
       caption = "Source: Wikipedia")

#plot_made
#nations arranged by rank
#try to make it interactive
```

The graph above is data from World Karate Championships 2021 Juniors. It was held in Cape Town, South Africa for Under 21. The brighter the blue in the graph, the more gold that country has won. The United States isn't as involved in karate hence why we have not received many medals. The highest total medals is France as depicted above. 


## Summary

Although karate is not a common sport in the Untied States, it is well known around the world. Throughout the years, participation has increased with more female students and instructors! There are many forms of Martial Arts such as Tae Kwon Do, Tang Soo Do, and Hapkido. The next World Karate Championships for Juniors is in 2023.

